\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-06-11 syntax.tex
Save. Add new section.
Save. Working on the example

The motivation for sealing judgement is acting like a syntactic sugar helpful for inheritance. Consider the scenario we have constructed a linkage meant to be a recursor $  .. (T : \bW(\sigma)) \vdash L : \cL(\tau)$. Now we extend $\sigma$ with more constructors into $\sigma'$, but we don't have any rules to transfer $L$ to the context of $\bW(\sigma')$. Thus the correct way is to construct $L$ in an \textit{sealed} context, $  .. (T : \cU) \vdash L : \cL(\tau)$, and single out the \textit{recursor term}  $.. (T : \bW(\sigma)), L : \cL(\tau) \vdash \ \text{ Recursor } \ T \ L .. : R $ also functioning as \textit{coverage checking}.
\YZ{Does coverage checking mean exhaustiveness checking?}\EDJreply{Yes. The one make sure every case is handled in pattern-matching. Do you want me to replace the terminology using exhaustiveness checking? }\YZreply{Yes, I think exhaustiveness is standard parlance.}
(Because we don't need to inherit coverage checking -- we should redo it in every linkage) Here, the recursor should also be \textit{seal-ed} so that every field is relying on an abstract, overridable recursor.
\YZ{I suppose the terminology 'sealing' is a reference to ML modules? In
ML, sealing has the connotation of hiding things behind an existential
type. So using the same word may cause the reader to have false
presumptions about what is going on here.}\EDJreply{You are right. Our "Sealing" is not hiding a particular field into an existential type, but our seal is make several fields together into an "existential type". Basically it hides the concrete definition of inductive type so that future fields doesn't have to be defined upon that.}\EDJreply{I will resolve this comment once I add the throughout example and you find it clear -- because I haven't changed any text}
Thus the sealing judgement will be helpful to shift the context from $.. (T : \bW(\sigma)) .. $ to $.. (T : \cU) ..$
\YZ{Can we have a more concrete example of how the judgment is useful?}\EDJreply{Working on it, don't resolve}

However, in most of the cases, we don't need to seal anything, and thus the "Seal-Id" is used. For notation clearance, we will sometime use $sf'$ to emphasize that we consider that seal $s$ as a term $(sf' \ s)$.

@@

>>>>

The motivation for sealing judgement is acting like a syntactic sugar helpful for inheritance -- due to the presence of inductive type in the context, not everything is inheritable. For example, $ X_1 : \bW \sigma_1 \vdash t : T$ in the parent family will generally not be able to be inherited to the children once we override the inductive type. In other words, there is no way ``transplanting'' $t$ into the context $X_2 : \bW \sigma_2$. This makes all the fields after this inductive type non-inheritable -- which shouldn't be the case because a lot of fields might not be directly relying on this concrete $\bW \sigma_1$.

Sealing is used to exploit this fact -- with sealing, we can add well-typed terms $X_1 : \cU \vdash t : T$, into the parent family, in the context of $ X_1 : \bW \sigma_1$. Later when we want to inherit $t$, because $t$ only consider $X_1$ as an arbitrary type, inheritance is plausible.

Of course, any fields using "Wsup" and "Wrec" directly relies on the $\bW(\sigma)$ and thus non-inheritable -- in these cases, "Wsup" can be understood as concrete constructors and "Wrec" are \textit{exhaustiveness checking}. These fields together with inductive types are the one sealing responsible for hiding. After compilation of linkage type into existential type, we can easily hide the textit{concrete} definition of the inductive type while exposing all the fields using "Wsup" and "Wrec" like an abstract interface. Apparently, future fields relies on this abstract interface will have no problem on inheritance. \YZ{Does coverage checking mean exhaustiveness checking?}\EDJreply{Yes. The one make sure every case is handled in pattern-matching. Do you want me to replace the terminology using exhaustiveness checking? }\YZreply{Yes, I think exhaustiveness is standard parlance.}
Of course, since "Wsup" and "Wrec" directly rely on the concrete inductive definition, we will have to override these fields whenever inductive type is overridden. For "Wsup" we only need to override each constructor and for "Wrec" it is just doing exhaustiveness checking inside each children family. The recursor handlers however, can be safely inherited.
\YZ{I suppose the terminology 'sealing' is a reference to ML modules? In
ML, sealing has the connotation of hiding things behind an existential
type. So using the same word may cause the reader to have false
presumptions about what is going on here.}\EDJreply{You are right. Our "Sealing" is not hiding a particular field into an existential type, but our seal is make several fields together into an "existential type". Basically it hides the concrete definition of inductive type so that future fields doesn't have to be defined upon that.}\EDJreply{I will resolve this comment once I add the throughout example and you find it clear -- because I haven't changed any text}

\YZ{Can we have a more concrete example of how the judgment is useful?}\EDJreply{Working on it, don't resolve}

However, there are cases we don't need to seal anything (i.e. doing exhaustiveness checking when using recursor), and thus the "Seal-Id" is used. For notation clearance, we will sometime use $sf'$ to emphasize that we consider that seal $s$ as a term $(sf' \ s)$.

@@

\subsection{Exemplar Usage of Meta Theory}
\input{syntactic-example.tex}
